Canadian Grocery Price Analysis

### 2024-12-04 paper/paper.qmd
Update paper.qmd

@@

# Data Details {#sec-data_details}

## Cleaning and Processing

The dataset was cleaned to focus on items with complete pricing and promotional information. Additional transformations included converting prices to numeric format and standardizing product categories.

```{r}
#| label: tbl-cleaned_data
#| tbl-cap: "Cleaned data for grocery price analysis"
#| echo: false

merged_data %>%
  head(10) %>%
  kable(
    col.names = c("Retailer", "Current Price", "Old Price", "Promotion", "Product Type"),
    booktabs = TRUE
  )
```

>>>>

@tbl-cleaned_data_summary showcases the cleaned dataset.

```{r}
#| label: tbl-cleaned_data_summary
#| tbl-cap: "Summary of Cleaned Dataset"
#| echo: false

@@
